---
title: "jealous_IOR"
author: "Sabrina Karl"
date: "4 12 2020"
output: html_document
---

---
title: "dog_jealousy_reli"
author: "Christoph Voelter"
date: "16/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(psych)
library(tidyverse)
library(irr)
```

Sniffing data
```{r}
setwd("C:/Users/karls/Documents/Laptop_backup_120319/DATADRIVE0/PhD/Studien/jealousy_behavioural/interreliability_coding/IOR_files_N=51")

sniffing.data <- read.table(file="sniffing_IOR_new.csv", header=T, sep=";")

cor.test(sniffing.data$Kristina, sniffing.data$Kata, method = "spearman", use ="complete.obs")


```
--> 0.89

Sniffing_anal_region
```{r}
sniffing_anal.data <- read.table(file="Sniffing_anal_region.csv", header=T, sep=";")

cor.test(sniffing_anal.data$Kristina, sniffing_anal.data$Kata, method = "spearman", use ="complete.obs")


```
--> 0.83

Blocking data
```{r}
blocking.data <- read.table(file="blocking_IOR_new.csv", header=T, sep=";")

#Agreement:
blocking.data%>%summarise(mean(ifelse(Kristina == Kata,1,0)))


cohen.kappa(cbind(blocking.data$Kristina,blocking.data$Kata))

icc(blocking.data, model="twoway", type="agreement")
```
--> 0.86


Dominant behaviors
```{r}
dom.data <- read.table(file="dominant_IOR.csv", header=T, sep=";")

dom.data%>%summarise(mean(ifelse(Kristina == Kata,1,0)))


cohen.kappa(cbind(dom.data$Kristina,dom.data$Kata))
```

--> Kappa = 0.27

Friendly behaviors towards all humans
```{r}
Frihum.data <- read.table(file="friendly_towards_human_all.csv", header=T, sep=";")

Frihum.data%>%summarise(mean(ifelse(Kristina == Kata,1,0)))


cohen.kappa(cbind(Frihum.data$Kristina,Frihum.data$Kata))
```
--> 0.80

Friendly behaviors towards stranger
```{r}
Fristr.data <- read.table(file="friendly_towards_stranger.csv", header=T, sep=";")

Fristr.data%>%summarise(mean(ifelse(Kristina == Kata,1,0)))


cohen.kappa(cbind(Fristr.data$Kristina,Fristr.data$Kata))
```
--> 0.94

Friendly behaviors towards caregiver
```{r}
Fricar.data <- read.table(file="friendly_towards_caregiver.csv", header=T, sep=";")

Fricar.data%>%summarise(mean(ifelse(Kristina == Kata,1,0)))


cohen.kappa(cbind(Fricar.data$Kristina,Fricar.data$Kata))
```
--> 0.82


Fake dog approach
```{r}
approach.data <- read.table(file="fake_dog_approach_IOR.csv", header=T, sep=";")

approach.data%>%summarise(mean(ifelse(Kristina == Kata,1,0)))

cohen.kappa(cbind(approach.data$Kristina,approach.data$Kata))
icc(ia.data, model="twoway", type="agreement")
```
lower estimate   upper
unweighted kappa -1.6e-08        0 1.6e-08
weighted kappa    0.0e+00        0 0.0e+00
--> ???
ICC 0.5?

fake dog IA
```{r}
ia.data <- read.table(file="fake_dog_IA_IOR_new.csv", header=T, sep=";")

ia.data%>%summarise(mean(ifelse(Kristina == Kata,1,0)))


cohen.kappa(cbind(ia.data$Kristina,ia.data$Kata))

icc(ia.data, model="twoway", type="agreement")
```
--> 0.52

Non offensive
```{r}
no.data <- read.table(file="non_offensive_IOR.csv", header=T, sep=";")

no.data%>%summarise(mean(ifelse(Kristina == Kata,1,0)))


cohen.kappa(cbind(no.data$Kristina,no.data$Kata))

icc(no.data, model="twoway", type="agreement")

```
--> 0.38


Behavioral categories
```{r}
bc.data <- read.table(file="attitude_category_IOR_new.csv", header=T, sep=";")
levels(bc.data$Kristina)
levels(bc.data$Kata)

cohen.kappa(cbind(bc.data$Kristina,bc.data$Kata))

#icc(no.data, model="twoway", type="agreement")
```
--> weighted kappa 0.79