---
title: "Dog Jealousy- analysis Script"
author: ""
date: "September 22, 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())


library(lme4)
library(tidyverse)
library(ggthemes)
library(psych)
library(summarytools)
library(cowplot)
library(glmmTMB)

#install.packages("")

#load(file ="mm1_mult_poss.RData")

library(exactRankTests)

better.wilcox2=function(var1, var2){
  test.data=data.frame(var1, var2)
  test.data=subset( test.data, var1 != var2)
  N=nrow(test.data)
  w.res=wilcox.exact (test.data$var1, test.data$var2, paired=T, exact=T, alternative = c("two.sided"))
  wT=w.res$statistic
  wT=max(c(wT, N*(N+1)/2- wT))
return(data.frame(T.plus=wT, N=N, P=w.res$p.value) )
}

source("./functions/diagnostic_fcns.r")
source("./functions/glmm_stability.r")
source("./functions/boot_glmm.r")
source("./functions/drop1_para.r")

```

Notes:
Maylo is doubled. Dusty has no values in reaction phase.


```{r loading data, include = FALSE}
orig.data <- read.csv(file="data/200915_beh_jealousy_Kata_coding_output_all_data_questionnaires.csv")
  
view(dfSummary(orig.data))

blocking.data<-orig.data %>%
  mutate(blocking = ifelse(Value=="Blocking",1,0), non_off_manipulation = ifelse(Value=="Non-offensive manipulation",1,0), dom_beh = ifelse(Value=="Dominant behaviours",1,0)) %>%
  group_by(subject, breed, condition, side_fakedog, side_chair) %>%
  summarise(blocking.sum=sum(blocking), non_off_manipulation.sum=sum(non_off_manipulation), dom_beh.sum=sum(dom_beh))%>%
  mutate(blocking_presence = ifelse(blocking.sum>0,1,0), non_off_manipulation_presence = ifelse(non_off_manipulation.sum>0,1,0), dom_beh_presence = ifelse(dom_beh.sum>0,1,0)) %>%
  ungroup()

table(blocking.data$condition, blocking.data$blocking_presence)
table(blocking.data$condition, blocking.data$non_off_manipulation_presence)
table(blocking.data$condition, blocking.data$dom_beh_presence)
```

####stop here#####




```{r loading data, include = FALSE}
cb.data <- read.csv(file="data/Action_understanding_counterbalancing.csv")%>%
   mutate(Trial = ifelse(Phase=="Test" & Trial=="1",9,ifelse(Phase=="Test" & Trial=="2",10,ifelse(Phase=="Test" & Trial=="3",11,ifelse(Phase=="Test" & Trial=="4",12,Trial)))))%>%
  mutate(Subject=recode(Subject, "Paolo"="Paulo"))%>%
  mutate(Test_condition=recode(Test_condition, Habituation="habituation"))%>%
  mutate(	Left_objet_color=recode(Left_objet_color, yellow="Yellow"))%>%
  mutate(Breed=recode(Breed, Australian_Shepherd="Australian_shepherd", Border_Collie="Border_collie", border_collie="Border_collie", Jack_Russell="Jack_russell", Siberian_Husky="Husky"))%>%
  droplevels()

view(dfSummary(cb.data))

str(orig.data)

str(cb.data)
levels(cb.data$Subject)
levels(orig.data$Subject)

```

Data preparation
```{r include=FALSE}

merged.data<-orig.data  %>% 
  filter(Behaviour =="Looking time")%>%
  group_by(Subject, Trial, Value)%>%
  summarise(sum.duration=sum(duration))%>%
  ungroup()%>%
  droplevels()%>%
  complete(Subject, Trial, Value ,fill=list(sum.duration=0))%>% #fill in 0s
  full_join(cb.data)%>%
  filter(Subject!="Angelo2",Subject!="Saari" )%>% #2 subjects removed due to experimenter error
  separate(Value, c("IP", "look"), sep="_") %>%
  mutate(gaze_congruency=ifelse((look=="Left" & Looking_side=="Left")|(look=="Right" & Looking_side=="Right"), "gaze_congruent",ifelse((look=="Left" & Looking_side=="Right")|(look=="Right" & Looking_side=="Left"), "gaze_incongruent",ifelse(look=="Central", "central",""))))%>%
  mutate(grasping_congruency=ifelse((look=="Left" & Grasping_side=="Left")|(look=="Right" & Grasping_side=="Right"), "grasping_congruent",ifelse((look=="Left" & Grasping_side=="Right")|(look=="Right" & Grasping_side=="Left"), "grasping_incongruent",ifelse(look=="Central", "central",""))))%>%
  droplevels()


view(dfSummary(merged.data))

#write.csv(merged.data, "data/merged_data.csv")
```


```{r}
xdata <- merged.data %>%
  group_by(Subject, Trial, Test_condition, IP)%>%
  summarise(ip.duration=sum(sum.duration))

merged.data <- merged.data %>%
  left_join(xdata)%>%
  mutate(prop.looking=sum.duration/ip.duration)
write.csv(merged.data, "data/merged_data.csv")
```
### Grasping IP - absolute
```{r fig.width=10}

plot.data.IPgrasping.absolute <-merged.data %>%
  filter(IP =="Grasping" & look!="Away" & Phase=="Test")%>%
    mutate(Test_condition=fct_recode(as.factor(Test_condition), "Kongruent"="congruent", "Inkongruent"="incongruent"))%>%
  group_by(Subject, Test_condition, Group)%>%
  summarise(sum.looking = sum(sum.duration))%>%
  group_by(Test_condition)%>%
  add_count(sum.looking)

plot.data.IPgrasping.absolute.summary <- plot.data.IPgrasping.absolute %>%
  group_by(Test_condition)%>%
  summarise(mean.looking = mean(sum.looking), median.looking=median(sum.looking), sd(sum.looking))

plot.data.IPgrasping.absolute.summary




p.graspingIP.absolute <- ggplot(
  data = plot.data.IPgrasping.absolute, aes(x = Test_condition, y = sum.looking)) +
  geom_boxplot(aes(group = Test_condition),width=0.9, outlier.colour="white")+
  geom_point(aes(group = Subject), size=plot.data.IPgrasping.absolute$n, alpha=0.1)+
  labs(x = "Bedingung", y = "Relative Blickzeit") +
  theme_few() 
p.graspingIP.absolute


t.test(plot.data.IPgrasping.absolute$sum.looking[plot.data.IPgrasping.absolute$Test_condition=="Kongruent"], plot.data.IPgrasping.absolute$sum.looking[plot.data.IPgrasping.absolute$Test_condition=="Inkongruent"], paired = TRUE, alternative = "two.sided")

  
```
### Grasping IP - relative
```{r fig.width=10}

plot.data.IPgrasping.relative <-merged.data %>%
  filter(IP =="Grasping" & look!="Away" & Phase=="Test")%>%
    mutate(Test_condition=fct_recode(as.factor(Test_condition), "Kongruent"="congruent", "Inkongruent"="incongruent"))%>%
  group_by(Subject, Test_condition, Group)%>%
  summarise(prop.looking = sum(prop.looking)/2)%>%
  group_by(Test_condition)%>%
  add_count(prop.looking)

plot.data.IPgrasping.relative.summary <- plot.data.IPgrasping.relative %>%
  group_by(Test_condition)%>%
  summarise(mean.looking = mean(prop.looking), median.looking=median(prop.looking), sd(prop.looking))

plot.data.IPgrasping.relative.summary




p.graspingIP.relative <- ggplot(
  data = plot.data.IPgrasping.relative, aes(x = Test_condition, y = prop.looking)) +
  geom_boxplot(aes(group = Test_condition),width=0.9, outlier.colour="white")+
  geom_point(aes(group = Subject), size=plot.data.IPgrasping.relative$n, alpha=0.1)+
  labs(x = "Bedingung", y = "Relative Blickzeit") +
  theme_few() 
p.graspingIP.relative


t.test(plot.data.IPgrasping.relative$prop.looking[plot.data.IPgrasping.relative$Test_condition=="Kongruent"], plot.data.IPgrasping.relative$prop.looking[plot.data.IPgrasping.relative$Test_condition=="Inkongruent"], paired = TRUE, alternative = "two.sided")

  
```

### Grasping IP
```{r fig.width=10}

plot.data1 <-merged.data %>%
  filter(IP =="Grasping" & (gaze_congruency=="gaze_congruent" | gaze_congruency=="gaze_incongruent" |gaze_congruency=="central")& Phase=="Test")%>%
  mutate(grasping_congruency=fct_recode(as.factor(grasping_congruency), "Ergr. Obj."="grasping_congruent", "Nicht ergr. Obj."="grasping_incongruent",  "Exp."="central"))%>%
  mutate(Test_condition=fct_recode(as.factor(Test_condition), "Kongruent"="congruent", "Inkongruent"="incongruent"))%>%
  group_by(Subject, Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  summarise(mean.prop.looking = mean(prop.looking))%>%
  group_by(Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  add_count(mean.prop.looking)

plot.data1.grasping.summary <- plot.data1 %>%
  group_by(Test_condition,  grasping_congruency)%>%
  summarise(mean.looking = mean(mean.prop.looking), median.looking=median(mean.prop.looking), sd(mean.prop.looking))

plot.data1.grasping.summary 




p.graspingIP.gazecongruency <- ggplot(
  data = plot.data1, aes(x = gaze_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = gaze_congruency),width=0.9, outlier.colour="white")+
  geom_point(aes(group = Subject), size=plot.data1$n, alpha=0.2)+
  labs(x = "Attended object", y = "Looking time") +
  theme_few() +
  facet_wrap(~Test_condition, ncol = 2)

p.graspingIP.gazecongruency


p.graspingIP.graspingcongruency <- ggplot(
  data = plot.data1, aes(x = grasping_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = grasping_congruency),width=0.9, outlier.colour="white")+
  geom_point(aes(group = Subject), size=plot.data1$n, alpha=0.1)+
  labs(x = "Blickrichtung", y = "Relative Blickzeit") +
  theme_few() +
  facet_wrap(~Test_condition, ncol = 2)

p.graspingIP.graspingcongruency

ggsave(p.graspingIP.graspingcongruency, filename = "graphs/action_understanding_graspingIP.png", width = 12, height = 6, scale = 0.6)
  
```

Plot only for grasp new group

```{r}

p.graspingIP.gazecongruency.groupNew <- ggplot(
  data = plot.data1%>%filter(Group=="1_Grasp_new"), aes(x = gaze_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = gaze_congruency))+
  labs(x = "Attended object", y = "Looking time") +
  theme_few() +
  facet_wrap(~Test_condition, ncol = 2)

p.graspingIP.gazecongruency.groupNew


p.graspingIP.graspingcongruency.groupNew <- ggplot(
  data = plot.data1%>%filter(Group=="1_Grasp_new"), aes(x = grasping_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = grasping_congruency))+
  labs(x = "Grasped object", y = "Looking time") +
  theme_few() +
  facet_wrap(~Test_condition, ncol = 2)+
  ggtitle("Grasp new group")

p.graspingIP.graspingcongruency.groupNew
  

```
Plot only for grasp old group
```{r}

p.graspingIP.gazecongruency.groupOld <- ggplot(
  data = plot.data1%>%filter(Group=="2_Grasp_old"), aes(x = gaze_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = gaze_congruency))+
  labs(x = "Attended object", y = "Looking time") +
  theme_few() +
  facet_wrap(~Test_condition, ncol = 2)

p.graspingIP.gazecongruency.groupOld


p.graspingIP.graspingcongruency.groupOld <- ggplot(
  data = plot.data1%>%filter(Group=="2_Grasp_old"), aes(x = grasping_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = grasping_congruency))+
  labs(x = "Grasped object", y = "Looking time") +
  theme_few() +
  facet_wrap(~Test_condition, ncol = 2)+
  ggtitle("Grasp old group")

p.graspingIP.graspingcongruency.groupOld
  

```

combine plots
```{r fig.height=8, fig.width=6}
plot_graspingIP_gaspingcongruency_groups <- plot_grid(p.graspingIP.graspingcongruency.groupNew, p.graspingIP.graspingcongruency.groupOld, nrow=2)

ggsave(plot_graspingIP_gaspingcongruency_groups, filename="graphs/plot_graspingIP_gaspingcongruency_groups.png")
```

#### T-test: looking time to the object grasped by the experimenter during the Grasping Interest Period compared between the two conditions

```{r}

plot.data1 <-merged.data %>%
  filter(IP =="Grasping" & (gaze_congruency=="gaze_congruent" | gaze_congruency=="gaze_incongruent" |gaze_congruency=="central")& Phase=="Test")%>%
  group_by(Subject, Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  summarise(mean.prop.looking = mean(prop.looking))%>%
  group_by(Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  add_count(mean.prop.looking)


tdata.grasping_congruent <- plot.data1%>%
  filter(grasping_congruency=="grasping_congruent")

t.test(tdata.grasping_congruent$mean.prop.looking[tdata.grasping_congruent$Test_condition=="congruent"], tdata.grasping_congruent$mean.prop.looking[tdata.grasping_congruent$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")


tdata.grasping_incongruent <- plot.data1%>%
  filter(grasping_congruency=="grasping_incongruent")

t.test(tdata.grasping_incongruent$mean.prop.looking[tdata.grasping_incongruent$Test_condition=="congruent"], tdata.grasping_incongruent$mean.prop.looking[tdata.grasping_incongruent$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")

tdata.grasping_central <- plot.data1%>%
  filter(grasping_congruency=="central")

t.test(tdata.grasping_central$mean.prop.looking[tdata.grasping_central$Test_condition=="congruent"], tdata.grasping_central$mean.prop.looking[tdata.grasping_central$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")

```
### central looks and grasping incongruent looks combined
```{r}
plot.data.IPgrasping.central.and.incongr.looks <-merged.data %>%
  filter(IP =="Grasping" & (grasping_congruency=="grasping_incongruent" |grasping_congruency=="central")& Phase=="Test")%>%
  group_by(Subject, Test_condition, Trial)%>%
  summarise(sum.looking = sum(prop.looking))%>%
  group_by(Subject, Test_condition)%>%
  summarise(mean.prop.looking = mean(sum.looking))%>%
  group_by(Test_condition)%>%
  add_count(mean.prop.looking)

t.test(plot.data.IPgrasping.central.and.incongr.looks$mean.prop.looking[plot.data.IPgrasping.central.and.incongr.looks$Test_condition=="congruent"], plot.data.IPgrasping.central.and.incongr.looks$mean.prop.looking[plot.data.IPgrasping.central.and.incongr.looks$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")

p.graspingIP.graspingincon.central <- ggplot(
  data = plot.data.IPgrasping.central.and.incongr.looks, aes(x = Test_condition, y = mean.prop.looking)) +
  geom_boxplot(aes(group = Test_condition))+
  geom_point(aes(group = Subject), size=plot.data.IPgrasping.central.and.incongr.looks$n, alpha=0.1)+
  geom_line(aes(group = Subject), alpha=0.15, lty=2)+
  labs(x = "Condition", y = "Proportion looking time") +
  theme_few()

p.graspingIP.graspingincon.central

```
### congruent looks 
```{r}
plot.data.IPgrasping.congr.looks <-merged.data %>%
  filter(IP =="Grasping" & (grasping_congruency=="grasping_congruent")& Phase=="Test")%>%
  group_by(Subject, Test_condition)%>%
  summarise(mean.prop.looking = mean(prop.looking))%>%
  group_by(Test_condition)%>%
  add_count(mean.prop.looking)

p.graspingIP.graspingcon <- ggplot(
  data = plot.data.IPgrasping.congr.looks, aes(x = Test_condition, y = mean.prop.looking)) +
  geom_boxplot(aes(group = Test_condition))+
  geom_point(aes(group = Subject), size=plot.data.IPgrasping.congr.looks$n, alpha=0.1)+
  geom_line(aes(group = Subject), alpha=0.15, lty=2)+
  labs(x = "Condition", y = "Proportion looking time") +
  theme_few()

p.graspingIP.graspingcon 

```

```{r}
pg.graspingIP <- plot_grid(p.graspingIP.graspingcon, p.graspingIP.graspingincon.central, labels = c("A", "B") )
pg.graspingIP
```



### Looking IP
```{r}

plot.data1.lookingIP <-merged.data %>%
  filter(IP =="Looking" & (gaze_congruency=="gaze_congruent" | gaze_congruency=="gaze_incongruent" |gaze_congruency=="central")& Phase=="Test")%>%
  group_by(Subject, Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  summarise(mean.prop.looking = mean(prop.looking))%>%
  group_by(Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  add_count(mean.prop.looking)


plot.data1.looking.summary <- plot.data1.lookingIP %>%
  group_by(Test_condition,  gaze_congruency)%>%
  summarise(mean.looking = mean(mean.prop.looking), median.looking=median(mean.prop.looking), sd.looking=sd(mean.prop.looking))

plot.data1.looking.summary 




p.lookingIP.gazecongruency <- ggplot(
  data = plot.data1.lookingIP, aes(x = gaze_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = gaze_congruency),width=0.9, outlier.colour="white")+
  geom_point(aes(group = Subject), size=plot.data1.lookingIP$n, alpha=0.2)+
  labs(x = "Attended object", y = "Looking time") +
  theme_few() +
  facet_wrap(~Test_condition, ncol = 2)

p.lookingIP.gazecongruency


```


#### T-test: looking time to the object grasped by the experimenter during the Looking Interest Period compared between the two conditions

```{r}

tdata.gaze_congruent.lookingIP <- plot.data1.lookingIP %>%
  filter(gaze_congruency=="gaze_congruent")

t.test(tdata.gaze_congruent.lookingIP$mean.prop.looking[tdata.gaze_congruent.lookingIP$Test_condition=="congruent"], tdata.gaze_congruent.lookingIP$mean.prop.looking[tdata.gaze_congruent.lookingIP$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")


tdata.gaze_incongruent.lookingIP <- plot.data1.lookingIP %>%
  filter(gaze_congruency=="gaze_incongruent")

t.test(tdata.gaze_incongruent.lookingIP$mean.prop.looking[tdata.gaze_incongruent.lookingIP$Test_condition=="congruent"], tdata.gaze_incongruent.lookingIP$mean.prop.looking[tdata.gaze_incongruent.lookingIP$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")

```
### central looks and grasping incongruent looks combined
```{r}
plot.data.IPlooking.central.and.incongr.looks <-merged.data %>%
  filter(IP =="Looking" & (gaze_congruency=="gaze_incongruent" |gaze_congruency=="central")& Phase=="Test")%>%
  group_by(Subject, Test_condition, Trial)%>%
  summarise(sum.looking = sum(prop.looking))%>%
  group_by(Subject, Test_condition)%>%
  summarise(mean.prop.looking = mean(sum.looking))%>%
  group_by(Test_condition)%>%
  add_count(mean.prop.looking)

t.test(plot.data.IPlooking.central.and.incongr.looks$mean.prop.looking[plot.data.IPlooking.central.and.incongr.looks$Test_condition=="congruent"], plot.data.IPlooking.central.and.incongr.looks$mean.prop.looking[plot.data.IPlooking.central.and.incongr.looks$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")

p.lookingIP.graspingincon.central <- ggplot(
  data = plot.data.IPlooking.central.and.incongr.looks, aes(x = Test_condition, y = mean.prop.looking)) +
  geom_boxplot(aes(group = Test_condition))+
  geom_point(aes(group = Subject), size=plot.data.IPlooking.central.and.incongr.looks$n, alpha=0.1)+
  geom_line(aes(group = Subject), alpha=0.15, lty=2)+
  labs(x = "Condition", y = "Proportion looking time") +
  theme_few()

p.lookingIP.graspingincon.central

```
```{r}
plot.data.IPlooking.congr.looks <-merged.data %>%
  filter(IP =="Looking" & (gaze_congruency=="gaze_congruent")& Phase=="Test")%>%
  group_by(Subject, Test_condition)%>%
  summarise(mean.prop.looking = mean(prop.looking))%>%
  group_by(Test_condition)%>%
  add_count(mean.prop.looking)

p.lookingIP.graspingcon <- ggplot(
  data = plot.data.IPlooking.congr.looks , aes(x = Test_condition, y = mean.prop.looking)) +
  geom_boxplot(aes(group = Test_condition))+
  geom_point(aes(group = Subject), size=plot.data.IPlooking.congr.looks $n, alpha=0.1)+
  geom_line(aes(group = Subject), alpha=0.15, lty=2)+
  labs(x = "Condition", y = "Proportion looking time") +
  theme_few()

p.lookingIP.graspingcon 

```

```{r}
pg.lookingIP <- plot_grid(p.lookingIP.graspingcon , p.lookingIP.graspingincon.central, labels = c("A", "B") )
pg.lookingIP
```


### Extend IP
```{r}

plot.data1.extendIP <-merged.data %>%
  filter(IP =="Extend" & (gaze_congruency=="gaze_congruent" | gaze_congruency=="gaze_incongruent")& Phase=="Test")%>%
  group_by(Subject, Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  summarise(mean.prop.looking = mean(prop.looking))%>%
  group_by(Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  add_count(mean.prop.looking)


p.extendIP.gazecongruency <- ggplot(
  data = plot.data1.extendIP, aes(x = gaze_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = gaze_congruency),width=0.9, outlier.colour="white")+
  geom_point(aes(group = Subject), size=plot.data1.extendIP$n, alpha=0.2)+
  labs(x = "Attended object", y = "Looking time") +
  theme_few() +
  facet_wrap(~Test_condition, ncol = 2)

p.extendIP.gazecongruency



```



#### T-test: looking time to the object grasped by the experimenter during the Extend Interest Period compared between the two conditions

```{r}

tdata.gaze_congruent.extendIP <- plot.data1.extendIP %>%
  filter(gaze_congruency=="gaze_congruent")

t.test(tdata.gaze_congruent.extendIP$mean.prop.looking[tdata.gaze_congruent.extendIP$Test_condition=="congruent"], tdata.gaze_congruent.extendIP$mean.prop.looking[tdata.gaze_congruent.extendIP$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")

tdata.gaze_incongruent.extendIP <- plot.data1.extendIP %>%
  filter(gaze_congruency=="gaze_incongruent")

t.test(tdata.gaze_incongruent.extendIP$mean.prop.looking[tdata.gaze_incongruent.extendIP$Test_condition=="congruent"], tdata.gaze_incongruent.extendIP$mean.prop.looking[tdata.gaze_incongruent.extendIP$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")


```

### Extend IP: comparison between attended and ignored object
```{r}

plot.data1.extendIP2 <-merged.data %>%
  filter(IP =="Extend" & (gaze_congruency=="gaze_congruent" | gaze_congruency=="gaze_incongruent")& Phase=="Test")%>%
  group_by(Subject, gaze_congruency)%>%
  summarise(mean.prop.looking = mean(prop.looking))%>%
  group_by( gaze_congruency)%>%
  add_count(mean.prop.looking)


p.extendIP.gazecongruency2 <- ggplot(
  data = plot.data1.extendIP2, aes(x = gaze_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = gaze_congruency),width=0.9, outlier.colour="white")+
  geom_point(aes(group = Subject), size=plot.data1.extendIP2$n, alpha=0.1)+
  labs(x = "Attended object", y = "Looking time") +
  theme_few()
p.extendIP.gazecongruency2



```

```{r}

t.test(plot.data1.extendIP2$mean.prop.looking[plot.data1.extendIP2$gaze_congruency=="gaze_congruent"], plot.data1.extendIP2$mean.prop.looking[plot.data1.extendIP2$gaze_congruency=="gaze_incongruent"], paired = TRUE, alternative = "two.sided")

```


### Approach IP
```{r}

plot.data1.approachIP <-merged.data %>%
  filter(IP =="Approach" & (gaze_congruency=="gaze_congruent" | gaze_congruency=="gaze_incongruent")& Phase=="Test")%>%
  group_by(Subject, Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  summarise(mean.prop.looking = mean(prop.looking))%>%
  group_by(Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  add_count(mean.prop.looking)

plot.data1.approachIP.summary <- plot.data1.approachIP%>%
  group_by(Test_condition, grasping_congruency)%>%
  summarise(mean.looking = mean(mean.prop.looking, na.rm=TRUE), median.looking=median(mean.prop.looking, na.rm=TRUE), sd.looking=sd(mean.prop.looking, na.rm=TRUE))

p.approachIP.gazecongruency <- ggplot(
  data = plot.data1.approachIP, aes(x = gaze_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = gaze_congruency),width=0.9, outlier.colour="white")+
  geom_point(aes(group = Subject), size=plot.data1.approachIP$n, alpha=0.2)+
  labs(x = "Attended object", y = "Looking time") +
  theme_few() +
  facet_wrap(~Test_condition, ncol = 2)

p.approachIP.gazecongruency


p.approachIP.graspingcongruency <- ggplot(
  data = plot.data1.approachIP, aes(x = grasping_congruency, y = mean.prop.looking)) +
  geom_boxplot(aes(group = grasping_congruency),width=0.9, outlier.colour="white")+
  geom_point(aes(group = Subject), size=plot.data1.approachIP$n, alpha=0.1)+
  labs(x = "Grasped object", y = "Looking time") +
  theme_few() +
  facet_wrap(~Test_condition, ncol = 2)

p.approachIP.graspingcongruency
  
```



#### T-test: looking time to the object grasped by the experimenter during the Extend Interest Period compared between the two conditions

```{r}

tdata.grasping_congruent.approachIP <- plot.data1.approachIP %>%
  filter(grasping_congruency=="grasping_congruent")

t.test(tdata.grasping_congruent.approachIP$mean.prop.looking[tdata.grasping_congruent.approachIP$Test_condition=="congruent"], tdata.grasping_congruent.approachIP$mean.prop.looking[tdata.grasping_congruent.approachIP$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")

tdata.grasping_incongruent.approachIP <- plot.data1.approachIP %>%
  filter(grasping_congruency=="grasping_incongruent")

t.test(tdata.grasping_incongruent.approachIP$mean.prop.looking[tdata.grasping_incongruent.approachIP$Test_condition=="congruent"], tdata.grasping_incongruent.approachIP$mean.prop.looking[tdata.grasping_incongruent.approachIP$Test_condition=="incongruent"], paired = TRUE, alternative = "two.sided")


```

```{r}
plot.data.central.looks <-merged.data %>%
  filter(IP =="Grasping" & (gaze_congruency=="gaze_congruent" | gaze_congruency=="gaze_incongruent")& Phase=="Test")%>%
  group_by(Subject, Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  summarise(mean.prop.looking = mean(prop.looking))%>%
  group_by(Test_condition, Group, gaze_congruency, grasping_congruency)%>%
  add_count(mean.prop.looking)
```

### Habituation

```{r}


plot.habituation.IPdata<-merged.data%>%
  filter(look!="Away")%>%
  filter(Test_condition=="habituation")%>%
  droplevels()%>%
  group_by(Subject, Test_condition,Trial, IP) %>% 
  summarize(Time = mean(sum.duration))%>%
  add_count(Time)


mean.habituation.IPdata <- plot.habituation.IPdata %>%
  group_by(Trial, IP) %>% 
  summarize(mean.Time = mean(Time))


p.hab.IP <- ggplot(
  data=plot.habituation.IPdata, aes(x=Trial, y=Time)) +   
  geom_point(aes(x=Trial, y=Time, group=Subject), size = plot.habituation.IPdata$n, colour = "darkgrey", alpha=0.4) +
  geom_line(aes(x=Trial, y=Time, group=Subject), lty=2, alpha=0.4)+
  geom_line(data=mean.habituation.IPdata, aes(x=Trial, y=mean.Time), lty=1, col="red", alpha=1)+
  #ylim(0,3)+
  labs(x="Trial number",y="Looking time")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))+   ggtitle("Habituation")+
  facet_wrap( ~ IP, ncol=2)

p.hab.IP 


```

```{r}

plot.habituation.data<-merged.data%>%
  filter(look!="Away")%>%
  filter(Test_condition=="habituation")%>%
  droplevels()%>%
  group_by(Subject, Test_condition,Trial, Breed, Sex) %>% 
  summarize(Time = sum(sum.duration))%>%
  add_count(Time)


mean.habituation.data <- plot.habituation.data %>%
  group_by(Trial) %>% 
  summarize(mean.Time = mean(Time))


p.hab <- ggplot(
  data=plot.habituation.data, aes(x=Trial, y=Time)) +   
  geom_point(aes(x=Trial, y=Time, group=Subject), size = plot.habituation.data$n, colour = "darkgrey", alpha=0.4) +
  geom_line(aes(x=Trial, y=Time, group=Subject), lty=2, alpha=0.4)+
  geom_line(data=mean.habituation.data, aes(x=Trial, y=mean.Time), lty=1, col="red", alpha=1)+
  #ylim(0,3)+
  labs(x="Trial number",y="Looking time")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))+   ggtitle("Habituation")

p.hab 


```

```{r eval=FALSE, echo=FALSE}


##Centering of factors for random slopes

plot.habituation.data$z.Trial=scale(plot.habituation.data$Trial)

```

```{r}

hist(plot.habituation.data$Time)


mm.hab=lmer(Time~z.Trial+
              (1+z.Trial|Subject)+(1+z.Trial|Breed),
              data=plot.habituation.data, REML=F)
ranef.diagn.plot(mm.hab)

diagnostics.plot(mm.hab)

summary(mm.hab)

drop1(mm.hab, test = "Chisq")


```
```{r}
boot.res <- boot.glmm.pred(
  model.res = mm.hab, excl.warnings = T,
  nboots = 1000, para = T, level = 0.95
)

boot.res
```



```{r}
boot.res.trial <- boot.glmm.pred(
  model.res = mm.hab, excl.warnings = T,
  nboots = 1000, resol = 384,  para = T, level = 0.95, use="z.Trial"
)
```

```{r}

plot.xvals=seq(from=min(plot.habituation.data$Trial), to=max(plot.habituation.data$Trial),
               length.out=384)

p.hab <- ggplot(
  data=plot.habituation.data, aes(x=plot.xvals)) +   
  geom_point(data=plot.habituation.data, aes(x=Trial, y=Time, group=Subject), size = plot.habituation.data$n, colour = "darkgrey", alpha=0.4) +
  #geom_line(data=plot.habituation.data, aes(x=Trial, y=Time, group=Subject), lty=2, alpha=0.4)+
  geom_line(data=mean.habituation.data, aes(x=Trial, y=mean.Time), lty=1, col="red", alpha=1)+
  geom_ribbon(data=boot.res.trial$ci.predicted, aes(x = plot.xvals, ymin=boot.res.trial$ci.predicted$lower.cl,
                                              ymax=boot.res.trial$ci.predicted$upper.cl), fill="grey", alpha=0.5)+
 geom_line(data=boot.res.trial$ci.predicted, aes(x = plot.xvals, y=boot.res.trial$ci.predicted$fitted), lty=2)+
  #ylim(0,3)+
  labs(x="Trial number",y="Looking time")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))+   ggtitle("Habituation")

p.hab 



```

### Comparison between last habituation trial and first test trial

```{r}
transition.data2 <- merged.data %>%
  filter(Trial==9 )%>%
  filter(IP=="Looking")%>%
  filter(gaze_congruency=="gaze_congruent")%>%
  select(Subject, IP, Group,   Test_condition )


transition.data <- merged.data %>%
  filter(Trial==8 |Trial==9 )%>%
  filter(IP=="Looking")%>%
  filter(look!="Away")%>%
  group_by(Subject,Phase, IP, Group)%>%
  summarise(sum.duration=sum(sum.duration))%>%
  select(Subject, Phase, IP, Group,  sum.duration )%>%
  spread(Phase, sum.duration)%>%
  full_join(transition.data2)%>%
  mutate(look_new_object=ifelse((Group=="1_Grasp_new" & Test_condition=="incongruent")|(Group=="2_Grasp_old" & Test_condition=="congruent"), "old_object",
                                ifelse((Group=="1_Grasp_new" & Test_condition=="congruent")|(Group=="2_Grasp_old" & Test_condition=="incongruent"), "new_object", "")))

  

t.test(transition.data$Habituation[transition.data$look_new_object=="new_object"], transition.data$Test[transition.data$look_new_object=="new_object"], paired = TRUE, alternative = "two.sided")

t.test(transition.data$Habituation[transition.data$look_new_object=="old_object"], transition.data$Test[transition.data$look_new_object=="old_object"], paired = TRUE, alternative = "two.sided")
```

Check whether the looking IP duration differs between last habituation and first test trial
```{r}
transition.data2 <- merged.data %>%
  filter(Trial==9 )%>%
  filter(IP=="Looking")%>%
  filter(gaze_congruency=="gaze_congruent")%>%
  select(Subject, IP, Group,   Test_condition )


transition.data <- merged.data %>%
  filter(Trial==8 |Trial==9 )%>%
  filter(IP=="Looking")%>%
  filter(look=="Away")%>%
  select(Subject, Phase, IP, Group,  ip.duration )%>%
  spread(Phase, ip.duration)%>%
  full_join(transition.data2)%>%
  mutate(look_new_object=ifelse((Group=="1_Grasp_new" & Test_condition=="incongruent")|(Group=="2_Grasp_old" & Test_condition=="congruent"), "old_object",
                                ifelse((Group=="1_Grasp_new" & Test_condition=="congruent")|(Group=="2_Grasp_old" & Test_condition=="incongruent"), "new_object", "")))

  

t.test(transition.data$Habituation[transition.data$look_new_object=="new_object"], transition.data$Test[transition.data$look_new_object=="new_object"], paired = TRUE, alternative = "two.sided")

t.test(transition.data$Habituation[transition.data$look_new_object=="old_object"], transition.data$Test[transition.data$look_new_object=="old_object"], paired = TRUE, alternative = "two.sided")
```
##relative looking time
```{r}
transition.data2 <- merged.data %>%
  filter(Trial==9 )%>%
  filter(IP=="Looking")%>%
  filter(gaze_congruency=="gaze_congruent")%>%
  select(Subject, IP, Group,   Test_condition )


transition.data <- merged.data %>%
  filter(Trial==8 |Trial==9 )%>%
  filter(IP=="Looking")%>%
  filter(look!="Away")%>%
  group_by(Subject,Phase, IP, Group)%>%
  summarise(prop.looking=sum(prop.looking))%>%
  select(Subject, Phase, IP, Group,  prop.looking )%>%
  spread(Phase, prop.looking)%>%
  full_join(transition.data2)%>%
  mutate(look_new_object=ifelse((Group=="1_Grasp_new" & Test_condition=="incongruent")|(Group=="2_Grasp_old" & Test_condition=="congruent"), "old_object",
                                ifelse((Group=="1_Grasp_new" & Test_condition=="congruent")|(Group=="2_Grasp_old" & Test_condition=="incongruent"), "new_object", "")))

  

t.test(transition.data$Habituation[transition.data$look_new_object=="new_object"], transition.data$Test[transition.data$look_new_object=="new_object"], paired = TRUE, alternative = "two.sided")

t.test(transition.data$Habituation[transition.data$look_new_object=="old_object"], transition.data$Test[transition.data$look_new_object=="old_object"], paired = TRUE, alternative = "two.sided")
```



```{r}

transition.plot.data <- transition.data%>%
  gather(phase, prop.look, Test, Habituation)%>%
  group_by(phase,look_new_object )%>%
  mutate(prop.look=round(prop.look,2))%>%
  add_count(prop.look)%>%
  ungroup()%>%
  mutate(phase=recode(phase, Test="Test trial 1", Habituation="Habituation trial 8"))%>%
  mutate(look_new_object=recode(look_new_object, new_object="New Object", old_object="Old Object"))

transition.plot.data.summary <- transition.plot.data%>%
    group_by(phase,look_new_object )%>%
    summarise(mean.looking = mean(prop.look, na.rm=TRUE ), median.looking=median(prop.look ), sd.looking=sd(prop.look ))
  

p.hab4 <- ggplot(
  data=transition.plot.data, aes(x=phase, y=prop.look, group=Subject)) +   
  geom_boxplot(aes(group=phase), width=0.9, outlier.colour="white")+
  geom_point( size = transition.plot.data$n,  alpha=0.4) +
  #geom_line( lty=2, alpha=0.4)+
  #ylim(0,3)+
  labs(x="",y="Relative Blickzeit")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10)) +
    facet_wrap( ~ look_new_object, ncol=2)
p.hab4 

```


